LAGOS lake depth

### 2020-03-24 README.Rmd
cleanup

Data Summary: [manuscript/data.pdf](manuscript/data.pdf)

@@

Tables: [manuscript/tables.pdf](manuscript/tables.pdf)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# see scripts/99_make_taxonomy.R
library(dplyr)
taxonomy <- read.csv("data/taxonomy.csv", 
                     stringsAsFactors = FALSE)
dt       <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", 
               stringsAsFactors = FALSE) %>%
  names() %>%  as.data.frame() %>%  setNames("col_name") %>%
  left_join(taxonomy) %>% data.frame() %>%
  dplyr::filter(!is.na(description)) %>%
  setNames(c("column name", "description"))

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# see scripts/99_make_taxonomy.R
dt <- read.csv("data/depth_predictors.csv", 
               stringsAsFactors = FALSE) %>% 
  names() %>%  as.data.frame() %>%  setNames("col_name") %>%
  left_join(taxonomy) %>% data.frame() %>%
  dplyr::filter(!is.na(description)) %>%
  setNames(c("column name", "description"))

>>>>

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
taxonomy <- read.csv("data/taxonomy.csv", 
                     stringsAsFactors = FALSE)

# see scripts/99_make_taxonomy.R
dt <- read.csv("data/depth_predictors.csv", 
               stringsAsFactors = FALSE) %>% 
  names() %>%  as.data.frame() %>%  setNames("col_name") %>%
  left_join(taxonomy) %>% data.frame() %>%
  dplyr::filter(!is.na(description)) %>%
  setNames(c("column name", "description"))

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# see scripts/99_make_taxonomy.R
dt       <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", 
               stringsAsFactors = FALSE) %>%
  names() %>%  as.data.frame() %>%  setNames("col_name") %>%
  left_join(taxonomy) %>% data.frame() %>%
  dplyr::filter(!is.na(description)) %>%
  setNames(c("column name", "description"))

@@
